---
title: "Coexpressalog_Integration_only_r"
output: coexpressalog_integration_only
---
Import Libaries


```{r}
library(scater)
library(Seurat)


library(SeuratDisk)
library(SeuratData)
library(patchwork)
```
Read in file and correct

Do preprocessing

```{r}

correct_integration_loom = Connect(filename = "~/passala/Generated_Tables/Temp_junk/slimmed_concatenated_rice_maize_genes_aligned_with_only_coexpressalogs.loom", mode = "r")

correct_integration_seurat = as.Seurat(correct_integration_loom)

correct_integration_seurat.list <- SplitObject(correct_integration_seurat, split.by = "Species")

correct_integration_seurat.list <- lapply(X = correct_integration_seurat.list, FUN = function(x) {
  x <- NormalizeData(x)
  x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 1000)
})

features <- SelectIntegrationFeatures(object.list = correct_integration_seurat.list)


```

do integration

```{r}

correct_integration_seurat.anchors <- FindIntegrationAnchors(object.list = correct_integration_seurat.list, anchor.features = features)


correct_integration_seurat.combined <- IntegrateData(anchorset = correct_integration_seurat.anchors)

DefaultAssay(correct_integration_seurat.combined) <- "integrated"

correct_integration_seurat.combined <- ScaleData(correct_integration_seurat.combined, verbose = FALSE)
correct_integration_seurat.combined <- RunPCA(correct_integration_seurat.combined, npcs = 30, verbose = FALSE)
correct_integration_seurat.combined <- RunUMAP(correct_integration_seurat.combined, reduction = "pca", dims = 1:20)
correct_integration_seurat.combined <- FindNeighbors(correct_integration_seurat.combined, reduction = "pca", dims = 1:30)
correct_integration_seurat.combined <- FindClusters(correct_integration_seurat.combined, resolution = 0.5)

```
plot
```{r}
p1 <- DimPlot(correct_integration_seurat.combined, reduction = "umap", group.by = "Species")
p2 <- DimPlot(correct_integration_seurat.combined, reduction = "umap", group.by = "Cell.Cluster.Annotation")
p1 + p2

```
Convert back to loom

```{r}
correct_integration_seurat.combined.loom <- as.loom(correct_integration_seurat.combined, filename = "~/passala/Generated_Tables/Temp_junk/integrated_by_default_seurat_only_coexpressalogs.loom", verbose = FALSE)
correct_integration_seurat.combined.loom
```
```{r}
correct_integration_seurat.combined.loom$close_all()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
